\cvsection{Projects}

% \setlength{\columnwidth}{540pt} % Adjust the column width
% \cvproject{title}{date}{location}{link}
\begin{multicols}{2} % Start two-column layout
    % \setlength{\columnsep}{20pt} % Adjust the column separation
    \cvproject{Game Engine}{2023}{HSE Course Project}{https://github.com/sdshorin/graphic_engine}
    \begin{itemize}
        \item Developed a game engine from scratch.
        \item Created a custom CPU renderer.
        \item Engine supports complex game scenes with animations.
    \end{itemize}

    \cvproject{ssl-md5}{January 2022}{42 School}{https://github.com/sdshorin/ft_ssl_md5}
    \begin{itemize}
        \item Constructed an encryption algorithm from scratch.
        \item Implemented hash functions: MD5, SHA256, SHA224, SHA512, SHA384, SHA512/256.
        \item Developed ciphers: Base64, DES, DES-ECB, DES-CBC.
    \end{itemize}
    
% \end{multicols}
% \begin{multicols}{2} % Start two-column layout
    \cvproject{Inception-of-Things}{February 2022}{42 School}{https://github.com/sdshorin/Inception-of-Things}
    \begin{itemize}
        \item Executed a foundational DevOps project using Kubernetes.
        \item Utilized tools such as Vagrant, K3S, K3D, and ArgoCD.
    \end{itemize}
    
\columnbreak
    \cvproject{HTTP Webserver in C++}{June 2022}{42 School}{https://github.com/sdshorin/webserv}
    \begin{itemize}
        \item Implemented an HTTP server using C++.
        \item Supported GET, POST, PUT, DELETE, and HEAD methods.
        \item Ensured resilience under heavy loads.
        \item Provided support for both static and CGI content.
    \end{itemize}

    \cvproject{Snake-sssembly-RISCV}{April 2023}{HSE}{https://github.com/sdshorin/snake-sssembly-RISCV}
    \begin{itemize}
        \item Developed a classic Snake game in RISC-V Assembly.
        \item Implemented low-level interrupt handling.
        \item Designed a memory-mapped I/O system.
        \item Achieved high-quality graphics with automatic background generation.
    \end{itemize}
\end{multicols}
